---
title: "Download"
---

```{r version_name_control, echo=FALSE}
# data directory
data_dir <- "_data"

# define version to append
new_version <- "_1.0.0"

# regular expression to match version pattern
version_pattern <- "_[0-9]+\\.[0-9]+\\.[0-9]+"  # Matches "_1.0.0", "_2.1.3", etc.

# list all csv files
files <- list.files(data_dir, pattern = "\\.csv$", full.names = TRUE)

# loop and rename files
for (file in files) {
  # define filename
  original_name <- basename(file)
  
  # check if already contains a version
  if (grepl(version_pattern, original_name)) {
    # if yes, replace with new version
    new_name <- sub(version_pattern, new_version, original_name)
  } else {
    # if no version append 
    new_name <- sub("\\.csv$", paste0(new_version, ".csv"), original_name)
  }
  
  # define full new path
  new_full_path <- file.path(dirname(file), new_name)
  
  # rename only if the name differs 
  if (original_name != new_name) {
    if (file.rename(file, new_full_path)) {
      cat("Renamed:", original_name, "to", new_name, "\n")
    } else {
      cat("Failed to rename:", original_name, "\n")
    }
  } else {
    cat("No change needed for:", original_name, "\n")
  }
}
```

## CSV
To download the database in csv format please use this link:

* [StatePol-CSV](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/StatePol/Database/tree/main/_data)

## R
To download the data in R, you can use the `read.csv` function from the base R library.

### Politician
```{r}
politician <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/politicians.csv")
```

### Mandate
```{r}
mandate <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/mandate.csv")
```

### PPG
```{r}
ppg <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/faction.csv")
```

### PPG-Leadership
```{r}
pggleadership <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/board.csv")
```

### Presidency
```{r}
presidency <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/presidium.csv")
```

### Committee
```{r}
committee <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/committee.csv")
```

### Cabinet
```{r}
cabinet <- 
  read.csv("https://raw.githubusercontent.com/StatePol/Database/main/_data/cabinet.csv")
```

## Checking the Database Version and Changelog

To ensure you are using the correct version of the StatePol database, please check the [VERSION](https://github.com/StatePol/Database/blob/main/VERSION) file in our repository for the current version number.

We recommend reviewing the [CHANGELOG](https://github.com/StatePol/Database/blob/main/CHANGELOG.md) to be aware of the changes, additions, or fixes in each version of the database.
